Connecting the Popularity Adjusted Block Model to the Generalized Random Dot Product Graph for Clustering and Parameter Estimation

### 2020-09-23 summary.Rmd
still wip

```{r}
import::here(cluster.pabm, .from = '~/dev/pabm-grdpg/functions.R')

@@

```{r}
# plot.A <- function(A, margins = c(0, 0, 0, 0)) {
#   default.mar <- par()$mar
#   par(mar = margins)
#   plot(A, border = NA, key = NULL, 
#        xlab = '', ylab = '', main = '',
#        axis.row = NULL, axis.col = NULL, asp = 1)
#   par(mar = default.mar)
# }

# plot.A <- function(A, labels) {
#   heatmap(A[order(labels), order(labels)],
#           margins = c(0, 0),
#           revC = TRUE)
# }

plot.A <- function(A, labels, max.size = 500) {
  # https://www.r-graph-gallery.com/79-levelplot-with-ggplot2.html
  A <- A[order(labels), order(labels)]
  n <- nrow(A)
  if (n > max.size) {
    ind <- sort(sample(seq(n), max.size))
    A <- A[ind, ind]
  }
  A %>% 
    tibble::as_tibble() %>% 
    tibble::rowid_to_column(var = 'X') %>% 
    tidyr::gather(key = 'Y', value = 'Z', -1) %>% 
    dplyr::mutate(Y = rev(as.numeric(gsub('V', '', Y)))) %>% 
    ggplot() + 
    geom_tile(aes(x = X, y = Y, fill = Z)) + 
    coord_fixed() + 
    labs(x = NULL, y = NULL) + 
    theme_void() + 
    theme(legend.position = 'none',
          axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank()) + 
    scale_x_continuous(expand = c(0, 0)) + 
    scale_y_continuous(expand = c(0, 0)) + 
    scale_fill_gradient(low = 'red', high = 'yellow')
}
```

@@

>>>>

```{r}
import::here(cluster.pabm, plot.A, .from = '~/dev/pabm-grdpg/functions.R')

@@

@@

In the third example,

```{r, cache = TRUE, fig.cap = 'Adjacency matrix of the Karnataka villages data, arranged by the clustering produced by Algorithm 2.'}
A.hh <- readRDS('data/village-hh-59.rds')
zhat.hh <- cluster.pabm(A.hh, 6)
plot.A(A.hh, zhat.hh)
```
